An approach for cloud correction of operational humidity channels

### 2020-09-10 Article/ici_submm_cloudcorr.tex
Changes in Sect. 4

\subsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]
	\label{tab:ICI_MWI_channels}	
	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range. The main objective of ICI is measure ice cloud properties and improve the representation of clouds in regional and global models. ICI is a conically scanning millimetre/sub-millimetre radiometer which will measure 13 frequencies from 183 GHz up to 664 GHz. Channels with centre frequencies 183.31, 325.15 and 448.0\,GHz are centered on water vapor absorption lines, and measure vertical polarization. While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization. 
In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard. MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements. The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments. The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_configuration}.

@@

For the structural parameters, the grid search is performed to determine the number of neurons (width) and hidden layers (depth). The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over the validation set. Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs, decay. The best performing hyperparameter configurations for a particular training set need not be same for other datasets. Therefore for each QRNN model used in this article the hyperparameters were tuned distinctly.

@@

\section{Cloud correction in  183 GHz channels}
%
\subsection{Training data}
%
Out of the 200\,000 ICI and MWI channel simulations, 150\,000 cases are randomly picked to form the training set. The rest are used for testing. In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database. ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise is added to the input training data according to the channel NE$\Delta$T. The target training data is kept noise free. In order to build a robust learning network, random noise is added to the inputs at each training iteration. This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples. The input data is also normalized with mean and standard deviation.
It is assumed for the simulations that the ICI and MWI channels are mapped to a common footprint and resolution. In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
\subsection{Training}
%
%t
\begin{table}[t]
\label{tab:QRNN_models}	
\caption{Summary of the different QRNN models used in the study.}
\begin{tabular}{lll}
\tophline
QRNN model & Training inputs & Target \\
\middlehline
QRNN-simple & I1V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I1V\\
			& I2V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I2V\\
			& I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I3V\\
			& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-15\\	
			& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-16\\
QRNN-all    & I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\

@@

To test if the uncertainty estimates given by QRNN are representative of prediction errors, we divided the $\pm2\sigma$ confidence interval into three bins and estimated the prediction error distribution for each. Figure~\ref{fig:error_distribution_uncertainty_bins_I1V} shows the prediction error distributions binned according to $2\sigma$ confidence interval for I1V, I2V and I3V. These results are from QRNN-simple. Similar results were also obtained for QRNN-all (figure not shown). Among the three channels the uncertainty in predictions for I1V and I2V are higher than I3V and an increase in the spread of errors with increasing uncertainty is evident in all three. As the errors increase, the spread is mostly symmetric around x-axis but among predictions associated with large uncertainties, high errors occur frequently. In other words, too-low/too-high QRNN predictions tend to be associated with high uncertainty.

Figure~\ref{fig:calibration_I2V} shows the calibration of prediction intervals on the test dataset for channel I2V. Results from both QRNN-simple and QRNN-all are shown. The calibration of predictions with correction greater than 5\,K is also shown. For the entire test dataset, the calibration curves for QRNN-simple and QRNN-all are quite identical. If cases with cloud correction greater than 5\,K are considered, the calibration curve for QRNN-simple lies  below y=x line, implying that the prediction intervals are overly narrow. A similar behaviour is observed for channel I3V (figure not shown). However, for channel I1V, both QRNN-all and QRNN-simple fail to provide well calibrated predictions for cases associated with high cloud impact.

These results show that both QRNN-simple and QRNN-all are successful in
providing well calibrated probabilistic predictions of the posterior
distributions except for few cases associated with high cloud impact. This is
not unexpected, as such cases form a small subset of the training set and their
priori distribution could be different from the the entire dataset. Since such
cases form only a fraction of the training dataset, it can be hard to train the
model to predict them accurately. A larger training dataset is needed to
increase the representation of such cases in QRNN.

\subsection{Discussion}

@@

\subsection{Data}
\subsubsection{Artic Weather Satellite}
The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
Earth Watch Programme Element. It is a small platform carrying a single
across-track scanning microwave radiometer. The main objective of AWS will be
to improve representation of Artic and sub-Arctic weather in NWP models and
improve the global weather forecasts. AWS will will have channels receiving
frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
detailed description of the AWS channels see \citep{eriksson2020study}, while a
brief summary of AWS channels relevant to this study are provided in
Table~\ref{tab:specifications_AWS}.

@@

\begin{table*}[t]
	\label{tab:ICI_MWI_channels}	
	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
	\begin{tabular}{lrr}
		\tophline
		Channel & Frequency 	& Bandwidth  \\
				& [GHz]			& [MHz]		\\
		\middlehline
		AWS-32	&	176.311    & 2000 		\\
		AWS-33	&	178.811    & 2000 		\\
		AWS-34	&	180.311    & 1000 		\\
		AWS-35	&	181.511    & 1000 		 \\
		AWS-36	&	182.311    & \phantom{0}500 	 \\
	    AWS-41    & 325.15$\pm$6.60    & 2800 \\
		AWS-42    & 325.15$\pm$4.10    & 1800  \\
		AWS-43    & 325.15$\pm$2.40    & 1200 \\
		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
			\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

\subsubsection{AWS simulations}
The satellite observations for AWS channels were simulated with ARTS. An similar ARTS set-up, as described for ICI (Section~\ref{sec:arts_simulations}) was followed, except that 24 monochromatic frequencies were used so that each channel could be represented with sufficient accuracy. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle. 125\,000 cases based on randomly selected CloudSat orbits were simulated.
\subsection{Training}
%
Out of the 125\,000 AWS simulations, 75\,000 cases are randomly picked to form the training set. The rest are used for testing. In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database. A similar data augmentation technique as described for ICI (Sec~\ref{sec:ici_training}) was followed to build a robust database and avoid memorisation of the samples.

For each 183\,GHz channel from AWS, a training scheme similar to QRNN-simple is used. For example, to
predict clear-sky TBs from AWS-34, the training data includes measurements AWS-34 and channels AWS-41, AWS-42, AWS-43, AWS-44. A grid search over the hyper-parameters was performed (results not shown) and the best performance over the validation set was obtained for 4 hidden layers with 128 neurons and batch size of 128 samples. Rectified Linear Unit (ReLU) was used as the activation function
\subsection{Prediction accuracy}
%f
\begin{figure}[t]
	\includegraphics[width = 80mm]{Figures/AWS-34_single.pdf}	
	\caption{Error distributions for AWS-34 predictions. Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' and  ``predicted(15\,K)''  refers to the datasets where cases with cloud correction greater than 5\,K and 15\,K are excluded, respectively.}
	\label{fig:qrnn_C34_deviations}	
\end{figure}
In an analogy between the results from ICI channels, we perform a similar error distribution analysis. Figure~\ref{fig:qrnn_C34_deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34. The statistics corresponding to curves are illustrated in Table~\ref{tab:statistics_qrnn_aws}. The label ``Filtered'' represents the subset where all cases with correction greater than 5\,K(15\,K) are removed. The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.30), however the  error distributions for the predictions are relatively symmetric. Removing cases with cloud correction greater than 5\,K, removes only 3.02\% of the data, but the errors reduce significantly. Infact, the standard deviation of predictions suggests that QRNN is successful in predicting the variability of noise-free simulations.

@@

\begin{table}[t]
	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions AWS channels. Results are from QRNN-simple. The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics. The fraction of cases removed by this filter are given in parentheses.}
	\label{tab:statistics_aws}
	\begin{tabular}{llrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-simple} \\
		\cline{3-7}
		%		\hline
		&&   Clear-sky &   All-sky &   		 All &   Filtered(5K)& Filtered(15K) \\
		\middlehline
AWS-32    &Bias     &   -0.00 &         -1.34 &           -0.08 &       		-0.07(5.30\%) & -0.08(2.50\%) \\
          &MAE      &    0.36 &          1.58 &            0.62 &        		 0.53 		  &	0.57	\\
          &STD      &    0.45 &          5.91 &            1.00 &        		 0.74 		  & 0.85\\
          &Skewness &    0.02 &         -7.48 &           -1.52 &       		-1.63 		  & -2.01\\
		\middlehline
AWS-33	  &Bias     &   -0.00 &         -0.98 &            0.01 &                 0.00(4.08\%)& 0.00(1.75\%)\\
		  &MAE      &    0.36 &          1.23 &            0.50 &                 0.43 	      & 0.46\\
		  &STD      &    0.45 &          4.70 &            0.77 &                 0.57 	      & 0.64\\
		  &Skewness &    0.01 &         -8.76 &           -0.40 &                -0.90  	  & -1.00\\

		\middlehline
AWS-34	  &Bias    &    0.00 &         -0.68 &            0.02 &                0.01(3.02\%)& 0.01(1.11\%) \\
		  &MAE      &    0.50 &          1.08 &            0.53 &                 0.47 		 & 0.50\\
		  &STD      &    0.63 &          3.69 &            0.78 &                 0.62 		 & 0.70\\
		  &Skewness &    0.02 &        -10.30 &           -0.34 &                -0.49 		 &-0.76	\\
		 \middlehline
AWS-35	 & Bias     &    0.00 &         -0.42 &            0.01 &                 0.01(1.92\%) & 0.01(0.70\%) \\
		 &MAE       &    0.50 &          0.83 &            0.50 &                 0.47 		   & 0.49\\
		 &STD       &    0.63 &          2.65 &            0.71 &                 0.60         & 0.65\\
		 &Skewness  &    0.01 &        -12.45 &           -0.15 &                -0.15         &-0.26\\
		 \middlehline
AWS-36   &Bias     &    0.00 &         -0.27 &            0.02 &                 0.02(1.30\%) & 0.02(0.31\%)\\
		 &MAE      &    0.70 &          0.90 &            0.67 &                 0.64 		  & 0.06\\
		 &STD      &    0.88 &          2.06 &            0.91 &                 0.81 		  &0.85\\
		 &Skewness &   -0.01 &        -12.00 &           -0.51 &                -0.15 		  &-0.12\\	 
		\bottomhline				
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
\subsubsection{Uncertainty quantification}
%f
\begin{figure}[t]
	\includegraphics[width = 80mm]{Figures/prediction_uncertainty_aws-34.pdf}	
	\caption{}
	\label{fig:prediction_uncertainty_aws-34}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
	\label{fig:uncertainty_cloud_impact}	
\end{figure}

In this section, we analyse the uncertainty estimates obtained from QRNN.  Figure~\ref{fig:prediction_uncertainty_aws-34} displays the prediction uncertainty in AWS-34 for different quantiles. The prediction uncertainty has been plotted as the deviation from the median value.  The different lines represent 1500 randomly chosen cases.  The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K, which is of the order of standard deviation of predictions for AWS-34 (see Table~\ref{tab:statistics_aws}). The high variability in the uncertainty estimates indicates that QRNN can successfully represent uncertainties for each case individually, rather than expressing them as a single measure for all cases. In the latter case, the uncertainty estimates would be concentrated along a narrow interval. Also, for majority of the cases, the prediction uncertainties are symmetric around the median, specially around  the 68\% ($\pm 1 \sigma$) and 94\% confidence interval ($\pm 2 \sigma$), suggesting that the posterior distribution follows a Gaussian distribution.

In order to analyse the performance of QRNN with task difficulty, the interrelation between the uncertainty estimates and cloud impact was investigated. Here we assume that cloud impact is representative of task difficulty. Fig~\ref{fig:uncertainty_cloud_impact} displays the plot between mean uncertainty estimates for $2\sigma$ confidence interval and the cloud impact. For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness. As fraction of cloud impact increases, the predictions become increasingly uncertain. However, this does not imply that the prediction accuracy is low. The calibration between prediction errors and measure of uncertainty should not be affected by task difficulty.

\subsubsection{Discussion}
%
The results demonstrate that QRNN is successful in predicting the clear-sky
noise-free data for AWS-33, AWS-34, AWS-35 and AWS-36 and partially for AWS-32. The prediction error distributions are symmetric with low bias and standard deviation. The cases with high error are mostly associated with high cloud impact and constitute only a small fraction of the total dataset. Excluding such cases decreases the variability in the predictions and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise. Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two ``super-channels''. Since the noise in the two channels are stationary and uncorrelated, the predictions benefit from the additional information, but the noise component tends to cancel out.

>>>>

\subsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]	
	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range. The main objective of ICI is measure ice cloud properties and improve the representation of clouds in regional and global models. ICI is a conically scanning millimetre/sub-millimetre radiometer which will measure 13 frequencies from 183 GHz up to 664 GHz. Channels with centre frequencies 183.31, 325.15 and 448.0\,GHz are centered on water vapor absorption lines, and measure vertical polarization. While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization. 
In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard. MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements. The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments. The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_channels}.

@@

For the structural parameters, the grid search is performed to determine the number of neurons (width) and hidden layers (depth). The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over the validation set. Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs, decay. The best performing hyperparameter configurations for a particular training set need not be same for other datasets. Therefore for each QRNN model used in this article, the hyperparameters were tuned distinctly.

@@

\section{Cloud correction in  183 GHz channels}
%
\subsection{Training data}
%
Out of the 200\,000 ICI and MWI channel simulations, 150\,000 cases are randomly picked to form the training set. The rest are used for testing. In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database. ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise is added to the input training data according to the channel NE$\Delta$T. The target training data is kept noise free. In order to build a robust learning network, random noise is added to the inputs at each training iteration. This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples. The input data is also normalized with mean and standard deviation.
It is assumed for the simulations that the ICI and MWI channels are mapped to a common footprint and resolution. In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
\subsection{Training}
\label{sec:ici_trainin}
%t
\begin{table}[t]
\caption{Summary of the different QRNN models used in the study.}
\label{tab:QRNN_models}
\begin{tabular}{lll}
\tophline
QRNN model & Training inputs & Target \\
\middlehline
QRNN-simple & I1V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I1V\\
			& I2V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I2V\\
			& I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I3V\\
			& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-15\\	
			& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-16\\
QRNN-all    & I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\

@@

To test if the uncertainty estimates given by QRNN are representative of prediction errors, we divided the $\pm2\sigma$ confidence interval into three bins and estimated the prediction error distribution for each. Fig.~\ref{fig:error_distribution_uncertainty_bins_I1V} shows the prediction error distributions binned according to $2\sigma$ confidence interval for I1V, I2V and I3V. These results are from QRNN-simple. Similar results were also obtained for QRNN-all (figure not shown). Among the three channels the uncertainty in predictions for I1V and I2V are higher than I3V and an increase in the spread of errors with increasing uncertainty is evident in all three. As the errors increase, the spread is mostly symmetric around x-axis but among predictions associated with large uncertainties, high errors occur frequently. In other words, too-low/too-high QRNN predictions tend to be associated with high uncertainty.

Fig.~\ref{fig:calibration_I2V} shows the calibration of prediction intervals on the test dataset for channel I2V. Results from both QRNN-simple and QRNN-all are shown. The calibration of predictions with correction greater than 5\,K is also shown. For the entire test dataset, the calibration curves for QRNN-simple and QRNN-all are quite identical. If cases with cloud correction greater than 5\,K are considered, the calibration curve for QRNN-simple lies  below y=x line, implying that the prediction intervals are overly narrow. A similar behaviour is observed for channel I3V (figure not shown). However, for channel I1V, both QRNN-all and QRNN-simple fail to provide well calibrated predictions for cases associated with high cloud impact.

These results show that both QRNN-simple and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact. This is not unexpected, as such cases form a small subset of the training set and their
priori distribution could be different from the the entire dataset. Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately. A larger training dataset would be required to increase the representation of such cases in QRNN.

@@

\subsection{Data}
\subsubsection{Artic Weather Satellite}
%t
\begin{table}[t]
	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
	\label{tab:specifications_AWS}	
	\begin{tabular}{lrr}
		\tophline
		Channel & Frequency 	& Bandwidth  \\
		& [GHz]			& [MHz]		\\
		\middlehline
		AWS-32	&	176.311    & 2000 		\\
		AWS-33	&	178.811    & 2000 		\\
		AWS-34	&	180.311    & 1000 		\\
		AWS-35	&	181.511    & 1000 		 \\
		AWS-36	&	182.311    & \phantom{0}500 	 \\
		AWS-41    & 325.15$\pm$6.60    & 2800 \\
		AWS-42    & 325.15$\pm$4.10    & 1800  \\
		AWS-43    & 325.15$\pm$2.40    & 1200 \\
		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
Earth Watch Programme Element. It is a small platform carrying a single
across-track scanning microwave radiometer. The main objective of AWS will be
to improve representation of Artic and sub-Arctic weather in NWP models and
improve the global weather forecasts. AWS will will have channels receiving
frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
detailed description of the AWS channels see \citet{eriksson2020study}, while a
brief summary of AWS channels relevant to this study are provided in
Table~\ref{tab:specifications_AWS}.

@@

\subsubsection{AWS simulations}
The satellite observations for AWS channels were simulated with ARTS. An similar ARTS set-up, as described for ICI (Sect.~\ref{sec:arts_simulations}) was followed, except that 24 monochromatic frequencies were used so that each channel could be represented with sufficient accuracy. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle. 125\,000 cases based on randomly selected CloudSat orbits were simulated.
\subsection{Training}
%
Out of the 125\,000 AWS simulations, 75\,000 cases are randomly picked to form the training set. The rest are used for testing. In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database. A similar data augmentation technique as described for ICI (Sec~\ref{sec:ici_training}) was followed to build a robust database and avoid memorisation of the samples.

For each 183\,GHz channel from AWS, a training scheme similar to QRNN-simple is used. For example, to
predict clear-sky TBs from AWS-34, the training data includes measurements AWS-34 and channels AWS-41, AWS-42, AWS-43, AWS-44. A grid search over the hyper-parameters was performed (results not shown) and the best performance over the validation set was obtained for 4 hidden layers with 128 neurons and batch size of 128 samples. Rectified Linear Unit (ReLU) was used as the activation function
\subsection{Prediction accuracy}
%f
\begin{figure}[t]
	\includegraphics[width = 80mm]{Figures/AWS-34_single.pdf}	
	\caption{Error distributions for AWS-34 predictions. Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' and  ``predicted(15\,K)''  refers to the datasets where cases with cloud correction greater than 5\,K and 15\,K are excluded, respectively.}
	\label{fig:qrnn_C34_deviations}	
\end{figure}
In an analogy between the results from ICI channels, we perform a similar error distribution analysis. Fig.~\ref{fig:qrnn_C34_deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34. The statistics corresponding to curves are provided in Table~\ref{tab:statistics_qrnn_aws}. The label ``Filtered'' represents the subset where all cases with correction greater than 5\,K(15\,K) are removed. The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.30), however the  error distributions for the predictions are relatively symmetric. Removing cases with cloud correction greater than 5\,K, removes only 3.02\% of the data, but the errors reduce significantly. Infact, the standard deviation of predictions suggests that QRNN is successful in predicting the variability of noise-free simulations.

@@

Overall the results demonstrate that QRNN is successful in predicting the clear-sky noise-free data for AWS-33, AWS-34, AWS-35 and AWS-36 and partially for AWS-32. The prediction error distributions are symmetric with low bias and standard deviation. The cases with high error are mostly associated with high cloud impact and constitute only a small fraction of the total dataset. Excluding such cases decreases the variability in the predictions and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise. Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two ``super-channels''. Since the noise in the two channels are stationary and uncorrelated, the predictions benefit from the additional information, but the noise component tends to cancel out. For AWS-32, QRNN is only partially successful in reducing the impact of hydrometeors. The prediction errors have significantly lower spread than the measurements, but cases with partially corrected cloud impact deteriorates the overall accuracy. Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, the testing data will inevitably contain cases for which QRNN has not trained for. Prediction for such \textit{out-of-distribution} cases would be inaccurate and highly uncertain. In such cases, the predictions should be used with caution.

\begin{table}[t]
	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions AWS channels. Results are from QRNN-simple. The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics. The fraction of cases removed by this filter are given in parentheses.}
	\label{tab:statistics_qrnn_aws}
	\begin{tabular}{llrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-simple} \\
		\cline{3-7}
		%		\hline
		&&   Clear-sky &   All-sky &   		 All &   Filtered(5K)& Filtered(15K) \\
		\middlehline
AWS-32    &Bias     &   -0.00 &         -1.34 &           -0.08 &       		-0.07(5.30\%) & -0.08(2.50\%) \\
          &MAE      &    0.36 &          1.58 &            0.62 &        		 0.53 		  &	0.57	\\
          &STD      &    0.45 &          5.91 &            1.00 &        		 0.74 		  & 0.85\\
          &Skewness &    0.02 &         -7.48 &           -1.52 &       		-1.63 		  & -2.01\\
		\middlehline
AWS-33	  &Bias     &   -0.00 &         -0.98 &            0.01 &                 0.00(4.08\%)& 0.00(1.75\%)\\
		  &MAE      &    0.36 &          1.23 &            0.50 &                 0.43 	      & 0.46\\
		  &STD      &    0.45 &          4.70 &            0.77 &                 0.57 	      & 0.64\\
		  &Skewness &    0.01 &         -8.76 &           -0.40 &                -0.90  	  & -1.00\\

		\middlehline
AWS-34	  &Bias    &    0.00 &         -0.68 &            0.02 &                0.01(3.02\%)& 0.01(1.11\%) \\
		  &MAE      &    0.50 &          1.08 &            0.53 &                 0.47 		 & 0.50\\
		  &STD      &    0.63 &          3.69 &            0.78 &                 0.62 		 & 0.70\\
		  &Skewness &    0.02 &        -10.30 &           -0.34 &                -0.49 		 &-0.76	\\
		 \middlehline
AWS-35	 & Bias     &    0.00 &         -0.42 &            0.01 &                 0.01(1.92\%) & 0.01(0.70\%) \\
		 &MAE       &    0.50 &          0.83 &            0.50 &                 0.47 		   & 0.49\\
		 &STD       &    0.63 &          2.65 &            0.71 &                 0.60         & 0.65\\
		 &Skewness  &    0.01 &        -12.45 &           -0.15 &                -0.15         &-0.26\\
		 \middlehline
AWS-36   &Bias     &    0.00 &         -0.27 &            0.02 &                 0.02(1.30\%) & 0.02(0.31\%)\\
		 &MAE      &    0.70 &          0.90 &            0.67 &                 0.64 		  & 0.06\\
		 &STD      &    0.88 &          2.06 &            0.91 &                 0.81 		  &0.85\\
		 &Skewness &   -0.01 &        -12.00 &           -0.51 &                -0.15 		  &-0.12\\	 
		\bottomhline				
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
\subsubsection{Uncertainty quantification}
%f
\begin{figure}[t]
	\includegraphics[width = 80mm]{Figures/prediction_uncertainty_aws-34.pdf}	
	\caption{The prediction uncertainty  for channel AWS-34  with respect to quantiles for randomly selected 1500 cases. The red line represents the uncertainty if underlying distribution is purely Gaussian with mean 270\,K and standard deviation 0.62\,K.}
	\label{fig:prediction_uncertainty_aws-34}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
	\label{fig:uncertainty_cloud_impact}	
\end{figure}

In this section, we analyse the uncertainty estimates obtained from QRNN.  Fig.~\ref{fig:prediction_uncertainty_aws-34} displays the prediction uncertainty in AWS-34 for different quantiles. The prediction uncertainty has been plotted as the deviation from the median value.  The different lines represent 1500 randomly chosen cases.  The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K, which is of the order of standard deviation of predictions for AWS-34 (see Table~\ref{tab:statistics_aws}). The high variability in the uncertainty estimates indicates that QRNN can successfully represent uncertainties for each case individually, rather than expressing them as a single measure for all cases. In the latter case, the uncertainty estimates would be concentrated along a narrow interval. Also, for majority of the cases, the prediction uncertainties are symmetric around the median, specially around  the 68\% ($\pm 1 \sigma$) and 94\% confidence interval ($\pm 2 \sigma$), suggesting that the posterior distribution follows a Gaussian distribution.
